\documentclass[11pt]{article}
\usepackage[margin=1in, top=1in]{geometry}
\usepackage[all]{nowidow}
\usepackage[hyperfigures=true, hidelinks, pdfhighlight=/N]{hyperref}
\usepackage[separate-uncertainty=true, group-digits=false]{siunitx}
\usepackage{graphicx,amsmath,physics,tabto,float,amssymb,pgfplots,verbatim,tcolorbox}
\usepackage{listings,xcolor,subcaption,caption,import,wrapfig,minted,biblatex}
\usepackage[version=4]{mhchem}
\usepackage[noabbrev]{cleveref}
\usepackage[british]{babel}
\newcommand{\creflastconjunction}{, and\nobreakspace}
\newcommand{\mb}[1]{\mathbf{#1}}
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}
\captionsetup{font=small, belowskip=0pt}
\pgfplotsset{compat=1.17}
\addbibresource{bibliography.bib}

\begin{document}

\begin{center}
    {\Large \textbf{Curriculum Vitae --- Miles Kidson}}

\end{center}

\section*{Contact Information}
\begin{itemize}
    \item Email: \texttt{miles.kidson@gmail.com}
    \item Cellphone: \texttt{079 620 6364}
\end{itemize}

\section*{Education}
\begin{itemize}
    \item Primary School: Newberry House Montessori School (2004 - 2010)
    \item High School:
    \begin{itemize}
        \item 2011 - 2012: Newberry House Montessori School
        \item 2013 - 2016: Stellenbosch Waldorf School
        \item 2017: Matric at Stellenbosch Waldorf School. 6 distinctions in English, Afrikaans, Maths, Geography, History, and Physical Sciences.
    \end{itemize}
    \item University
    \begin{itemize}
        \item 2019 - 2021: BSc with majors in Physics and Applied Maths at the University of Cape Town
        \begin{itemize}
            \item 2019: Dean's List
            \begin{itemize}
                \item PHY1004W: First Class
                \item MAM1000W: First Class
                \item MAM1043H: First Class
                \item MAM1044H: Second Class, Division One
                \item CSC1015F: First Class
                \item CSC1016S: First Class
            \end{itemize}
            \item 2020: No numerical marks were awarded, only pass/fail
            \begin{itemize}
                \item PHY2004W: Pass
                \item MAM2000W: Pass
                \item MAM2046W: Pass
            \end{itemize}
            \item 2021: 
            \begin{itemize}
                \item MAM3040W: Second Class, Division One
                \item PHY3004W: Second Class, Division Two
            \end{itemize}
            \item 2022: Honours in Physics, still in progress. I am working with Assoc. Prof. Zinhle Buthelezi and Assoc. Prof. Thomas Dietel in the ALICE experiment at CERN. 
        \end{itemize}
    \end{itemize}
\end{itemize}

\section*{Skills}
\begin{itemize}
    \item Proficient in coding in Python primarily for data analysis. 
    \item Using the ALICE O2 analysis framework, written in C\texttt{++} and ROOT for large-scale particle physics analysis.
    \item General Java and C\texttt{++} coding capabilities.
    \item Googling coding questions
\end{itemize}

\section*{Extras}
\begin{itemize}
    \item I tutored PHY1031F and PHY1032S in 2022
    \item In 2018 I went on a gap year to Europe, working on farms and travelling around France and the UK.
    \item I have a black belt in Karate-Jutsu.
    \item I play guitar and piano, and work at the Makhanda Jazz Festival in June/July every year.
\end{itemize}

\end{document}